\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-21 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.tex
Adding New Table

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 1.00 & 0.53 & 1.40\\
\hline
Bottom-up & 1.76 & 0.64 & 2.72\\
\hline
MinT(Shrink) & 0.74 & 0.51 & 1.10\\
\hline
OLS & 0.51 & 0.39 & 0.66\\
\hline
WLS & 1.21 & 0.58 & 1.74\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 1.00 & 0.99 & 1.01\\
\hline
Bottom-up & 1.42 & 1.18 & 1.80\\
\hline
MinT(Shrink) & 0.97 & 0.93 & 1.03\\
\hline
OLS & 0.97 & 0.96 & 0.98\\
\hline
WLS & 1.08 & 0.98 & 1.21\\
\hline
\end{tabular}

@@

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 1.00 & 0.63 & 1.37\\
\hline
Bottom-up & 1.73 & 0.75 & 2.57\\
\hline
MinT(Shrink) & 0.75 & 0.61 & 1.03\\
\hline
OLS & 0.54 & 0.46 & 0.74\\
\hline
WLS & 1.20 & 0.69 & 1.67\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 1.00 & 0.98 & 1.04\\
\hline
Bottom-up & 1.35 & 1.16 & 1.63\\
\hline
MinT(Shrink) & 0.93 & 0.91 & 0.99\\
\hline
OLS & 0.97 & 0.96 & 1.01\\
\hline
WLS & 1.04 & 0.96 & 1.14\\
\hline
\end{tabular}

>>>>

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\\hline
Base & 1.00 & 0.53 & 1.40\\ \hline
Bottom-up & 1.76 & 0.64 & 2.72\\ \hline
MinT(Shrink) & 0.74 & 0.51 & 1.10\\\hline
OLS & 0.51 & 0.39 & 0.66\\\hline
WLS & 1.21 & 0.58 & 1.74\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\\hline
Base & 1.00 & 0.99 & 1.01\\\hline
Bottom-up & 1.42 & 1.18 & 1.80\\\hline
MinT(Shrink) & 0.97 & 0.93 & 1.03\\\hline
OLS & 0.97 & 0.96 & 0.98\\\hline
WLS & 1.08 & 0.98 & 1.21\\\hline
\end{tabular}

@@

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\\hline
Base & 1.00 & 0.63 & 1.37\\\hline
Bottom-up & 1.73 & 0.75 & 2.57\\\hline
MinT(Shrink) & 0.75 & 0.61 & 1.03\\\hline
OLS & 0.54 & 0.46 & 0.74\\\hline
WLS & 1.20 & 0.69 & 1.67\\\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 1.00 & 0.98 & 1.04\\\hline
Bottom-up & 1.35 & 1.16 & 1.63\\\hline
MinT(Shrink) & 0.93 & 0.91 & 0.99\\\hline
OLS & 0.97 & 0.96 & 1.01\\\hline
WLS & 1.04 & 0.96 & 1.14\\\hline
\end{tabular}

### 2020-01-21 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Adding New Table

@@

>>>>

\usepackage{dcolumn}
\newcolumntype{d}[1]{D{.}{.}{#1}}

@@

\begin{table}[!b]
\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series. Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}. Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
\label{tab:Results_MSE}
\setlength{\tabcolsep}{7pt}
\centering
  \begin{tabular}{ld{3.2}d{3.2}d{3.2}d{3.2}d{3.2}d{3.2}}
    \toprule
    \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
    \multicolumn{3}{c}{Box-Cox Transformation}\\
    \cmidrule(lr){2-4} \cmidrule(lr){5-7}
    Method & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} \\
    & & \multicolumn{1}{c}{(Method-1)} & \multicolumn{1}{c}{(Method-2)} && \multicolumn{1}{c}{(Method-1)} &\multicolumn{1}{c}{(Method-2)}\\ \midrule
              & \multicolumn{6}{c}{ME}\\\cmidrule(lr){2-7}
    Base      & 1.00 & 0.53^{\ast\dag} & 1.40^{\ast\dag} & 1.00 & 0.63^{\ast\dag} & 1.37^{\ast\dag}\\
    OLS       & 0.51^{\ast} & 0.39^{\ast} & 0.66 & 0.54^{\ast} & 0.46^{\ast} & 0.74\\
    MinT      & 0.74 & 0.51^{\ast\dag} & 1.10^{\dag} & 0.75 & 0.61^{\ast} & 1.03^{\dag}\\
    WLS       & 1.21 & 0.58^{\ast\dag} & 1.74^{\ast\dag} & 1.20 & 0.69^{\ast\dag} & 1.67^{\ast\dag}\\
    Bottom-up & 1.76^{\ast} & 0.64^{\ast\dag} & 2.72^{\ast\dag} & 1.73 & 0.75^{\ast\dag} & 2.57^{\ast\dag}\\
              & \multicolumn{6}{c}{MSE}\\\cmidrule(lr){2-7}
    Base      & 1.00 & 0.99 & 1.01 & 1.00 & 0.98 & 1.04\\
    OLS       & 0.97^{\ast} & 0.96^{\ast} & 0.98^{\ast} & 0.97^{\ast} & 0.96^{\ast} & 1.01\\
    MinT      & 0.97^{\ast} & 0.93^{\ast} & 1.03 & 0.93^{\ast} & 0.91^{\ast} & 0.99\\
    WLS       & 1.08 & 0.98 & 1.21 & 1.04 & 0.96 & 1.14\\
    Bottom-up & 1.42 & 1.18 & 1.80 & 1.35 & 1.16 & 1.63\\
    \bottomrule
  \end{tabular}
\end{table}
